Why Donors Donate?

### 2020-08-25 analysis/05_market_simulator.Rmd
Reformatted the RenderPlotly

---
title: "Market Simulator"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
runtime: shiny
---

@@

    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_pref] <- 1

    beta_persona$p1_value[beta_persona$levels %in% input$p1_national_news] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_international_news] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_news_medium] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_follow_gov] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_travel_developing] <- 1

    # beta_persona$p1_value[beta_persona$levels == "Political Preference"] <- 1

    beta_persona$p1_value[beta_persona$levels %in% input$p1_institution_trust] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_others_charitable] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_worship_attendence] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion_importance] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_charity_importance] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_trust_in_charity] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_donation_frequency] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_donation_amount] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_volunteer_12] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_volunteer_frequency] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_personal_activism] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_family_activism] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_religious_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_sport_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_art_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_labor_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_environmental_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_professional_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_humanitarian_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_consumer_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_other_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_gender] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_marital_status] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_education] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_income] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_race] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_age] <- 1

@@

    beta_persona$p3_value[beta_persona$levels %in% input$p3_national_news] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_international_news] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_news_medium] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_follow_gov] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_travel_developing] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_political_pref] <- 1
    # 
    # beta_persona$p3_value[beta_persona$levels == "Political Preference"] <- input$p3_political_pref

    beta_persona$p3_value[beta_persona$levels %in% input$p3_institution_trust] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_others_charitable] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_worship_attendence] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion_importance] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_charity_importance] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_trust_in_charity] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_donation_frequency] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_donation_amount] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_volunteer_12] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_volunteer_frequency] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_personal_activism] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_family_activism] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_religious_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_sport_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_art_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_labor_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_political_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_environmental_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_professional_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_humanitarian_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_consumer_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_other_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_gender] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_marital_status] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_education] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_income] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_race] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_age] <- 1
    beta_persona

@@

# reactive slider input ----

@@

Market Share Per Persona
--------------------------------------

@@

  ggplotly(df %>% filter(Type == "Market Share") %>%
             mutate(
               Organization = factor(Organization, levels = c(input$ai_id, input$gp_id, input$ox_id, input$rc_id), ordered = TRUE),
               Persona = factor(Persona, levels = c(input$p1_id, input$p2_id, input$p3_id), ordered = TRUE)) %>% 
             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
             geom_bar(position = "dodge", stat = "identity") +
             labs(x="") + 
             scale_fill_manual(values = c( "#FFC30B", "#006633", "#660000")) +
             theme(legend.position = "right")
    )
})

>>>>

---
title: "Why Donors Donate?"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
runtime: shiny
---

@@

    beta_persona$p1_value[beta_persona$levels %in% input$p1_national_news] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_international_news] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_news_medium] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_follow_gov] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_travel_developing] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_pref] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_institution_trust] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_others_charitable] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_worship_attendence] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion_importance] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_charity_importance] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_trust_in_charity] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_donation_frequency] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_donation_amount] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_volunteer_12] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_volunteer_frequency] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_personal_activism] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_family_activism] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_religious_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_sport_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_art_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_labor_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_environmental_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_professional_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_humanitarian_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_consumer_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_other_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_gender] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_marital_status] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_education] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_income] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_race] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_age] <- 1

@@

    beta_persona$p3_value[beta_persona$levels %in% input$p3_national_news] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_international_news] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_news_medium] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_follow_gov] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_travel_developing] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_political_pref] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_institution_trust] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_others_charitable] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_worship_attendence] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion_importance] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_charity_importance] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_trust_in_charity] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_donation_frequency] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_donation_amount] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_volunteer_12] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_volunteer_frequency] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_personal_activism] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_family_activism] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_religious_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_sport_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_art_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_labor_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_political_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_environmental_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_professional_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_humanitarian_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_consumer_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_other_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_gender] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_marital_status] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_education] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_income] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_race] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_age] <- 1
    beta_persona

@@

@@

Market Share
--------------------------------------

@@

  ggplotly(df %>% filter(Type == "Market Share") %>%
             mutate(
               Organization = factor(Organization, levels = c(input$ai_id, input$gp_id, input$ox_id, input$rc_id), ordered = TRUE),
               Persona = factor(Persona, levels = c(input$p1_id, input$p2_id, input$p3_id), ordered = TRUE)) %>% 
             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
             geom_bar(position = "dodge", stat = "identity") +
             labs(x="", y = "Market Share") + 
             scale_fill_manual(values = c( "#FFC30B", "#006633", "#660000")) +
             theme(legend.position = "right",
                   panel.background = element_blank(),
                   panel.grid.major.y = element_line(color = "#D3D3D3"))
    )
})
